---
title: "2 Sample T-Test - Exercise"
output: html_notebook
---

Source of Data Frame

```{r}
df <- read.csv("T Test - 2.csv")
print(head(df))
```

feature = penjualan.sebelum.latihan as Data Frame 1 (df1)

```{r}
df1 <- df[2]
head(df1)
```

feature = penjualan.setelah.latihan as Data Frame 2 (df2)

```{r}
df2 <- df[3]
head(df2)
```

# Hypothesis

* H<sub>0</sub> = There is no significant difference of performance between employee before they receive sales training and employee after they receive sales training. (Accepted if p-value > 0.05)
* H<sub>1</sub> = There is a significant difference of performance between employee before they receive sales training and employee after they receive sales training. (Accepted if p-value < 0.05)

# Inferential Statistics

We will use 2 Sample T-Test because we only 2 raw data.

```{r}
hasil <- t.test(df2, df1)
print(hasil)
```

```{r}
p.value <- hasil[["p.value"]]
print(p.value)
```

```{r}
before <- hasil[["estimate"]][["mean of y"]]
after <- hasil[["estimate"]][["mean of x"]]
boost <- ((after - before)/before)*100
boost.amount <- (paste(boost, "%"))
print(boost.amount)
```

```{r}
terminated <- df[(df1>df2), 1]
print(terminated)
```

# Conclusion

1. is there any significant difference of performance after the employee receive sales training?

        So, the conclusion is that **there is a significant difference** of performance between employee before they receive sales training and employee after they receive sales training. Because `r p.value` is smaller than 0.05.

2. If there is a difference, is it better or worse?

        It is better, because the performance average has boosted `r boost.amount` compared to their performance average before receive sales training. (mean x > mean y)

3. Should we continue this training?

        Yes, because there is a significant difference after they receive this training and it boosted the performance by `r boost.amount`.

4. Who should be terminated to increase efficiency in sales team?

        The salesman number `r terminated` who should be terminated because his performance is declined after sales training.


***


```{r}
plot(density(df$penjualan.sebelum.latihan),
     col = rgb(1, 0, 0, 1),
     main = "Comparison",
     xlim = c(0, 10),
     ylim = c(0, 0.7))
par(new = TRUE)
plot(density(df$penjualan.setelah.latihan),
     col = rgb(1, 1, 0, 1),
     main = "",
     xlim = c(0, 10),
     ylim = c(0, 0.7))
```

