---
title: "Sample T-Test "
output: html_notebook
---

Source of Data Frame

```{r}
df <- read.csv("T Test - 1.csv")
head(df)
```



```{r}
df1 <- df[3]
head(df1)
```

Last Year Average

```{r}
last.year.average <- 6.7
print(last.year.average)
print(mean(df$nilai_sd_jogja))
```

# Hypothesis

* H<sub>0</sub> = There is no significant correlation between last year data average and this year data average. (Accepted if p-value > 0.05)
* H<sub>1</sub> = There is a significant correlation between last year data average and this year data average. (Accepted if p-value < 0.05)

# Inferential Statistics

We will use 1 Sample T-Test because we only use 1 reference data and 1 raw data.

```{r}
#print(t.test(raw.data, mu = reference.data))
print(t.test(df1, mu = last.year.average))
```

Since p-value: 0.51 is larger than alpha: 0.05, the conclusion is that there is no significant correlation between last year data average and this year data average.

***